Paper_analyses

### 2021-08-04 Paper_Analyses_subj_obje_arousal.Rmd
Update Paper_Analyses_subj_obje_arousal.Rmd

# Valence and arousal
```{r}

@@

@@

```
  # xlim(0,6)+
  facet_grid(~mediansplit_sample_valence2)
# plot separatelly

>>>>

# Valence and arousal - ridge
```{r}

@@

# lassomodels$firt

ridgemodels<-list()

# ridge
unique(db_new$exp)
# "3b" "3b"
db_full4new_stim_screen_pupil_nopract
unique(db_new$exp)

db_new_exp3b<- subset(db_full4new_stim_screen_pupil_nopract, 
                                     ssid_num< 500)

pp_id_3b<- unique(db_new_exp3b$ssid)

db_new_exp3b$ar_x_val<- db_new_exp3b$arousal_c* db_new_exp3b$valence_c

db_new_exp3b_1 <- select(db_new_exp3b, c(ssid, arousal_c, valence_c, ar_x_val, Mean_gray_z,pup_basCor))
i = 10
?glmnet::cv.glmnet
set.seed(808)

cv_fits_3b<- list(list())
cv_fits<-list(list())
library(glmnet)

for (i in pp_id_3b) {
  temp_3b <- subset(db_new_exp3b_1, ssid == 304)
  # cv_fits <- list(i)
  cv_fits_3b[[i]]<- list(cv.glmnet(as.matrix(temp_3b[,2:5]),temp_3b$pup_basCor, 
                                alpha = 0, nfolds = 8))

  cv_fits[[i]]<- list(glmnet(as.matrix(temp_3b[,2:5]),temp_3b$pup_basCor,
                             family = "gaussian",
                             alpha = 0, lambda = cv_fits_3b[[i]][[1]]$lambda.min))
  }

coef(cv_fits_3b[[i]][[1]], s = cv_fits_3b[[i]][[1]]$lambda.min)

coef(cv_fits[[i]][[1]], s = cv_fits[[i]][[1]]$lambda)
# 5 x 1 sparse Matrix of class "dgCMatrix"
#                       1
# (Intercept)  0.57036534
# arousal_c    0.34759064
# valence_c    0.34825059
# ar_x_val    -0.03044521
# Mean_gray_z -0.22724284

my_vector_ar<- vector(mode="numeric")
i

plot(cv_fits[["306"]][[1]])

plot(cv_fits[[2]][[1]])
plot(cv_fits[[2]][[1]],xvar="lambda",label=TRUE)
fit3=glmnet(x,g4,family="multinomial")
plot(cv_fits[[2]][[1]],pch=19)

View(my_vectors)
for (i in pp_id_3b) {
my_vector_ar[i]<- coef(cv_fits[[i]][[1]], s = cv_fits[[i]][[1]]$lambda)[2] # 3 is gender sd
}

my_vector_vl<- vector(mode="numeric")
# non gender sd
for (i in pp_id_3b) {
my_vector_vl[i]<- coef(cv_fits[[i]][[1]], s = cv_fits[[i]][[1]]$lambda)[3] 
}

# status
my_vector_ar_vl<- vector(mode="numeric")

for (i in pp_id_3b) {
my_vector_ar_vl[i]<- coef(cv_fits[[i]][[1]], s = cv_fits[[i]][[1]]$lambda)[4] 
}

# physical
my_vector_gray<- vector(mode="numeric")

for (i in pp_id_3b) {
my_vector_gray[i]<- coef(cv_fits[[i]][[1]], s = cv_fits[[i]][[1]]$lambda)[5] 
}

t.test(my_vector_ar)
# t = 41.071, df = 42, p-value < 0.00000000000000022
t.test(my_vector_vl)
# t = 34.501, df = 42, p-value < 0.00000000000000022

t.test(my_vector_ar_vl)
# t = -16.486, df = 42, p-value < 0.00000000000000022

t.test(my_vector_gray)
# t = -62.057, df = 42, p-value < 0.00000000000000022
```

@@

```
  # xlim(0,6)+
  facet_grid(~mediansplit_sample_valence2)
```{r}
# plot separatelly
